Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-04-26 analysis/paper/paper.Rmd
Cambia a CMAP
#21

Temperature data used are from NOAA's Merged Land Ocean Global Surface Temperature Analysis V4.0.1 [@smith2008; @vose2012], which blends land surface air temperature and sea surface (water) temperature analysis into a monthly global grid 5\degree\ longitude by 5\degree\ latitude. Monthly rainfall fields at 0.5\degree\ longitude by 0.5\degree\ latitude data from the Global Precipitation Climatology Centre [@schneider2015;@schneider2017] are also considered. The rainfall dataset is based on station-based records, and thus it only has continental coverage.

@@

## Availability of data and material {-}

All data used in this paper is freely available from their respective sources. ERA5 data can be obtained via the Copernicus Climate Data Store (https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means). NOAAGlobalTemp and GPCC precipitation data can be obtained through the NOAA Physical Sciences Laboratory website (https://psl.noaa.gov/data/gridded/data.noaaglobaltemp.html and https://psl.noaa.gov/data/gridded/data.gpcc.html). The Oceanic Niño Index is available via NOAA's Climate Prediction Center: https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt

## Code availability {-}

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at https://github.com/eliocamp/asymsam.

>>>>

Temperature data used are from NOAA's Merged Land Ocean Global Surface
Temperature Analysis V4.0.1 [@smith2008; @vose2012], which blends land surface
air temperature and sea surface (water) temperature analysis into a monthly
global grid 5\degree longitude by 5\degree latitude. For precipitation data we
used monthly data from the CPC Merged Analysis of Precipitation [\@xie1997],
with a 2.5\\degree\\ resolution in latitude and longitude. This rainfall gridded
dataset is based on information from different sources such as rain gauge
observations, satellite inferred estimations and the NCEP-NCAR reanalysis, and
it is available since 1979 to present.

@@

## Availability of data and material {.unnumbered}

All data used in this paper is freely available from their respective sources.
ERA5 data can be obtained via the Copernicus Climate Data Store
([<https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means>](https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means){.uri}).
CMAP Precipitation data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado,
USA, from their Web site at <https://psl.noaa.gov/data/gridded/data.cmap.html>.
The Oceanic Niño Index is available via NOAA's Climate Prediction Center:
<https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt>

## Code availability {.unnumbered}

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at https://github.com/eliocamp/asymsam.
including the code used to download the data can be found at
<https://github.com/eliocamp/asymsam>.
